---
title: "Ariana Bardauil's CV"
author:
  firstname: Ariana
  lastname: Bardauil
  address: "Buenos Aires, Argentina"
  position: "Data Scientist・Political Science"
  contacts:
    - icon: fa envelope
      text: arianabardauil@gmail.com
      url: "mailto:arianabardauil@gmail.com"
    - icon: assets/icon/bi-house-fill.svg
      text: my portfolio
      url: https://ariibard.github.io
    - icon: fa brands github
      text: GitHub
      url: https://github.com/ariibard
    - icon: fa brands linkedin
      text: LinkedIn
      url: https://linkedin.com/in/ariana-bardauil
    - icon: fa phone
      text: +54 9 11 3051 1306
      url: ninguno 
style:
  color-accent: 6a1f9a
format:
  awesomecv-typst:
    font-paths: ["assets/fonts/"]
    keep-typ: true
execute: 
  echo: false
  warning: false
---
```{r}
library(typstcv)
library(tidyverse)
```

## Education

```{r echo = FALSE}
#| output: asis
educ <- read.csv("data/education.csv",
                 colClasses = c("character", "Date", "Date", "character", "character"))

educ |>
  format_date(end = "end", sort_by = "start") |>
  resume_entry(title = "degree",
               description = "institution",
               details = "detail")
```

## Professional Training

```{r}
#| output: asis

pt <- read.csv("data/professional_training.csv",
                 colClasses = c("character", "Date", "Date", "character", "character"))

pt |>
  format_date(end = "end", sort_by = "start") |>
  typstcv::resume_entry(title = "title",
               description = "institution")
```

## Work experience

```{r}
#| output: asis

we <- read.csv("data/experiencia_laboral.csv",
                 colClasses = c("character", "Date", "Date", "character", "character", "character"))

we |>
  format_date(end = "end", sort_by = "start") |>
  typstcv::resume_entry(title = "position",
               description = "organization",
               details = c("description1", "description2"),
               location = "location")
```

## Teaching experience

```{r}
#| output: asis

te <- read.csv("data/teaching_experience.csv",
                 colClasses = c("character", "Date", "Date", "character", "character", "character")) 
te |>
  format_date(end = "end", sort_by = "start") |>
  typstcv::resume_entry(title = "position",
               description = "institution",
               details = c("description"),
               location = "location")
```


## Community Involvement

**R en Buenos Aires – Organizer & Instructor **  
[R en Buenos Aires](https://github.com/renbaires) is a local data science community that promotes the use of R in Spanish-speaking academic, public sector, and civil society contexts. The group organizes regular workshops, talks, and collaborative study spaces, 


**Núcleo de Innovación Social – Organizer (2023 – present)**  
The [Núcleo de Innovación Social](https://nucleodeinnovacionsocial.com.ar/) is a collective focused on the ethical, political, and methodological challenges of data use in the public sphere. It brings together professionals from government, academia, and activism to co-create visualizations, applied research, and public communication tools.

## Publications

```{r}
publis <- read.csv("data/publications.csv")
```

### Conference papers

```{r}
#| output: asis
publis[publis$type == "Conference paper", ] |>
  resume_entry(title = "title",
               description = "detail",
               details = "coauthors",
               date = "date")
```

### Technical reports

```{r}
#| output: asis

publis[publis$type == "Technical report", ] |>
  resume_entry(title = "title",
               description = "detail",
               details = "coauthors",
               date = "date")
```

### Book Chapter

```{r}
#| output: asis
publis[publis$type == "Book chapter", ] |>
  resume_entry(title = "title",
               description = "detail",
               details = "coauthors",
               date = "date")
```


### Conference Presentations

```{r}
#| output: asis

publis[publis$type == "Conference presentation", ] |>
  resume_entry(title = "title",
               description = "detail",
               details = "coauthors",
               date = "date")
```

## Research Experience

### Current

```{r}
#| output: asis

inv <- read.csv("data/investigacion.csv",
                 colClasses = c("character", "Date", "Date", "character", "character", "character", "character")) 


inv |> 
  filter(end > Sys.Date())|>
  format_date(end = "end", sort_by = "start") |>
  resume_entry(title = "role",
               description = "project",
               location = "institution",
               details = "description",
               date = "date") 
```

### Previus

```{r}
#| output: asis

inv |> 
  filter(end < Sys.Date())|>
  format_date(end = "end", sort_by = "start") |>
  resume_entry(title = "role",
               description = "project",
               location = "institution",
               details = "description",
               date = "date")

```


## Skills

```{r}
#| output: asis


skills <- read.csv("data/skills.csv") 

skills|>
  resume_entry(title = "area",
               description = "skills")
```